---
title: "PRROC Gating - NMA - Dynamic Borrowing" 
date: "`r format(Sys.time(), '%d %B, %Y')`"
author: "Anh Nguyen Duc"
output:
  html_document:
    toc: yes
    toc_float: true
    to_depth: 5
    collapsed: false
    smooth_scroll: false
    number_sections: true
    theme: united
    self_contained: false
  word_document: default
header-includes: \usepackage{docmute}
classoption: landscape
---

```{r setup, include=FALSE}
remove(list=ls())
knitr::opts_chunk$set(echo = TRUE)
# Load packages ----------------------------------------------------------------
require(tidyverse)
require(knitr)
require(R2WinBUGS)
require(pbugs) # parallel winbugs
require(R2jags)# parallel already supported
require(coda)  # nice mcmc utilities
require(mcmcplots) # nice mcmc utilities
require(readxl)
require(kableExtra)
require(extraDistr)
require(LaplacesDemon) # Student t Distribution: Precision Parameterization
```

## Utility functions
```{r echo=TRUE}
wald.ci <- function(x, n, ci.lev=.95) {
  p <- x/n
  se<- sqrt(p*(1-p)/n)
  z <- qnorm((1+ci.lev)/2) %>% abs
  p + c(-1,1)*z*se
}
#-------------------------------------------------------------------------------
lor.sd <- function(s1, n1, s2, n2) { 
# get log OR and SD
  f1 <- n1 - s1
  f2 <- n2 - s2
# x - matrix of two columns of successes (s) and failures (f)
  x <- rbind(c(s1, f1), 
             c(s2, f2))
  D <- factor(c("s","f"), levels=c("f","s"))
  m <- glm(x~D, family=binomial) %>% summary
  m$coefficients[2,1:2]
}
#-------------------------------------------------------------------------------
lhr.sd <- function(hr, low, upp) {
# approx log HR and SD 
  loghr <- log(hr)
  sd <- ((log(c(low,upp)) - loghr) / qnorm(.975)) %>% abs %>% sqrt %>% mean
  return(c("loghr"=loghr, "sd"=sd))
}
```

## Posterior probability of ``true'' response $\ge$ a threshold

### Load data
```{r echo=TRUE}
data.raw <- readxl::read_xlsx(path = 'PRROC.xlsx', range = cell_cols('A:M'))
data.use <- data.raw %>% dplyr::filter(dynamic_borrow_SAT=='Y')
data.use <- data.use[,c(1:3, data.use%>%ncol)]
data.use <- data.use[-2,,drop=F] # as per clinical team => remove Adavo
data.use %>% kbl() %>% kable_styling()
```

### WinBUGs model for binary EXNEX model with dynamic (stochastic) mixture weights

This is based on section 5.3 of https://onlinelibrary.wiley.com/action/downloadSupplement?doi=10.1002%2Fpst.1730&file=pst1730-sup-0001-supplementary.pdf 

Original paper is https://onlinelibrary.wiley.com/doi/epdf/10.1002/pst.1730

```{r echo=TRUE}
### Model definition when mixture weights are stochastic
binary_exnex_model_dw <- function() {
## Data to be specify in the input
#-------------------------------------------------------------------------------

# Nexch        - number of exchangeable components
# Nmix         - number of mixture weights and must be Nexch+1
# Nstrata      - number of strata e.g. studies or cohort (in platform trial)
# pMix         - matrix of Nmix * Nstrata mixture weights (each col summing up to 1)
# n            - vector of Nstrata elements storing patient numbers for each stratum
# r            - vector of Nstrata elements storing response numbers for each stratum

# mu.mean      - vector of Nexch prior mean(s)
# mu.prec      - vector of Nexch prior precision(s)
# tau.HN.scale - scale parameter of Half-Normal prior for tau
# ------- no longer needed -----------------------------------------------------
# nex.mean     - prior mean for non-exchangeable component
# nex.prec     - prior precision for non-exchangeable component
# ------- end of no longer needed ----------------------------------------------
# p.cut        - clinically relevant threshold for response rate to compare against
  
## Parameter(s) to be monitored
# p            - posterior response rate
# logit_p      - logit(p) i.e. log odd
# p.success    - posterior indicator if p > p.cut
# p.failure    - posterior indicator if p < p.cut
# pMix         - posterior mixture weight to test for "exchangeability"

#-------------------------------------------------------------------------------
  
  # prior distributions for EX-parameters
  for (jj in 1:Nexch) {
    mu[jj] ~dnorm(mu.mean[jj],mu.prec[jj])
    prior.tau.prec[jj] <- pow(tau.HN.scale[jj],-2)
    tau[jj] ~ dnorm(0,prior.tau.prec[jj]);I(0.001,)
    prec.tau[jj] <- pow(tau[jj],-2)
  }
  
  # log-odds parameters under EX
  for (jj in 1:Nexch) {
    for (j in 1:Nstrata) {
      re[jj,j] ~ dnorm(0,prec.tau[jj])
      LogOdds[jj,j] <- mu[jj]+re[jj,j]
    }
  }
  
  # log-odds parameters under NEX
  for (j in 1:Nstrata) {
    #p_Nmix[j] ~ dbeta(2,2) # slight mod to have flat prior
    #LogOdds[Nmix,j] ~ dnorm(nex.mean,nex.prec)#<- logit(p_Nmix[j])#

    # LogOdds[Nmix,j] ~ dt(0, 2, 1) #Student's t-distribution becomes the Cauchy distribution when the degrees of freedom is equal to one
    LogOdds[Nmix,j] ~ dunif(-20, 20)
    
  }
  
  # latent mixture indicators:
  # exch.index: categorial 1,...,Nmix=Nexch+1
  # exch: Nstrata x Nmix matrix of 0/1 elements
  for (j in 1:Nstrata) {
    exch.index[j] ~ dcat(pMix[1:Nmix,j])
    for (jj in 1:Nmix) {
      exch[j,jj] <- equals(exch.index[j],jj)
    }
  }
  
  # pick theta
  for (j in 1:Nstrata) {
    theta[j] <- LogOdds[exch.index[j],j]
  }
  
  # likelihood part
  for (i in 1:Nstrata) {
    logit( p[i] ) <- theta[i]
    p.success[i]  <- step(p[i]-p.cut)
    p.failure[i]  <- step(p.cut-p[i])
    r[i] ~ dbin(p[i],n[i])
    logit_p[i] <- theta[i]
  }
  
  # normalized mixture weights
  for (i in 1:Nstrata) {
    for (j in 1:Nmix) {
      pMix0[j,i] ~ dbeta(2, 2)
    }
  
    for (j in 1:Nmix) {
      pMix[j,i] <- pMix0[j,i] / sum(pMix0[,i])
    }    
  }

  
} # end of binary_exnex_model_dw

write.model(binary_exnex_model_dw, 'binary_exnex_model_dw.bug')

### Parameters to monitor
parameters_binary_exnex_model_dw <- c('p', 'logit_p', 'pMix', 'p.success', 'p.failure')

### Data

## EX part
mu.mean <- c(logit(.05), logit(.3)) # ex prior for hyper meanis centered at logit(0.05)
# ex precision  for hyperpar mean based on (23) of https://onlinelibrary.wiley.com/action/downloadSupplement?doi=10.1002%2Fpst.1730&file=pst1730-sup-0001-supplementary.pdf
mu.prec <- 1/sqrt( ( 1/inv.logit(mu.mean) + 1/(1-inv.logit(mu.mean)) )) # still missing s^2 but this would only make the prior more non-informative

Nexch   <- mu.mean %>% length

tau.HN.scale <- rep(1, Nexch)

# ## NEX part - no longer needed
# nex.mean<-logit(.15) # prior mean for nex part
# 
# # prior precision for nex part based on (20) of https://onlinelibrary.wiley.com/action/downloadSupplement?doi=10.1002%2Fpst.1730&file=pst1730-sup-0001-supplementary.pdf
# nex.prec <- 1/sqrt( 1/inv.logit(nex.mean) + 1/(1-inv.logit(nex.mean))  * 1e5 ) 

p.cut<-.15

Nmix    <- Nexch + 1

obs.orrs <- c(.05, .1, .15, .2, .25, .3, .35) # would-be observed ORR from expansion cohort
npt      <- 25 # number of patients from expansion cohort

data_binary_exnex_model_dw <- binary_exnex_jag_dw <- binary_exnex_mcmc_dw <- list()


## Run JAGs
for (id in 1:length(obs.orrs)) {
  
  print(paste0('Observed ORR = ', obs.orrs[id]))
  
  orr <- obs.orrs[id]
  n   <- c(data.use$n_a, npt)
  r   <- c(data.use$res_a, orr*npt) %>% round
  
  Nstrata <- n %>% length
  
  data_binary_exnex_model_dw[[id]]<- list(Nexch=Nexch, Nmix=Nmix, Nstrata=Nstrata,
                                          n=n, r=r,
                                          mu.mean=mu.mean, mu.prec=mu.prec,
                                          tau.HN.scale=tau.HN.scale,
                                          # nex.mean=nex.mean, nex.prec=nex.prec, 
                                          p.cut=p.cut
                                          )
  ### Inits
  inits_binary_exnex_model_dw <- function() {
    pMix0 <- rbeta(Nmix*Nstrata, 2, 2) %>% matrix(nrow=Nstrata) %>% t
    for (nc in 1:ncol(pMix0)) {
      pMix0[,nc] <- pMix0[,nc] / sum(pMix0[,nc])
    }
    
    list(
      "mu"=rnorm(Nexch),
      "tau"=rnorm(Nexch) %>% abs,
      "pMix0"=pMix0
      )  
  } # end of inits_binary_exnex_model_dw  
  
  # JAGS
  set.seed(36)
  binary_exnex_jag_dw[[id]] <- jags(data = data_binary_exnex_model_dw[[id]], 
                                  inits = inits_binary_exnex_model_dw, 
                                  parameters.to.save = parameters_binary_exnex_model_dw,
                                  model.file = "binary_exnex_model_dw.bug",
                                  n.chains=3, n.iter=1e4, n.burnin=5e3)
  # print(binary_exnex_jag_dw)
  
  binary_exnex_mcmc_dw[[id]] <- binary_exnex_jag_dw[[id]] %>% as.mcmc.rjags
  binary_exnex_mcmc_dw[[id]] %>% summary %>% print
  
  ### Credible interval for selected parameters
  mcmcplots::caterplot(binary_exnex_jag_dw[[id]], parms = c('p'))  
  
  ### Density plot for posterior logit alone
  par(ask=F)
  mcmcplots::denplot(binary_exnex_jag_dw[[id]], parms = c(paste0('logit_p[', Nstrata, ']')), collapse = T, lwd=2,xlim=c(-15,15), style ='plain', main='Posterior distribution of true ORR', frame.plot=F)
  
} # end of for (id in 1:length(obs.orrs))



### Run MCMC
```

### WinBUGs model for binary EXNEX model with fixed mixture weights

This is based on section 5.3 of https://onlinelibrary.wiley.com/action/downloadSupplement?doi=10.1002%2Fpst.1730&file=pst1730-sup-0001-supplementary.pdf 

Original paper is https://onlinelibrary.wiley.com/doi/epdf/10.1002/pst.1730

```{r echo=TRUE}
### Model definition when mixture weights are stochastic
binary_exnex_model_fw <- function() {
## Data to be specify in the input
#-------------------------------------------------------------------------------

# Nexch        - number of exchangeable components
# Nmix         - number of mixture weights and must be Nexch+1
# Nstrata      - number of strata e.g. studies or cohort (in platform trial)
# n            - vector of Nstrata elements storing patient numbers for each stratum
# r            - vector of Nstrata elements storing response numbers for each stratum

# mu.mean      - vector of Nexch prior mean(s)
# mu.prec      - vector of Nexch prior precision(s)
# tau.HN.scale - scale parameter of Half-Normal prior for tau
# ------- no longer needed -----------------------------------------------------
# nex.mean     - prior mean for non-exchangeable component
# nex.prec     - prior precision for non-exchangeable component
# ------- end of no longer needed ----------------------------------------------
# p.cut        - clinically relevant threshold for response rate to compare against
  
## Parameter(s) to be monitored
# p            - posterior response rate
# logit_p      - logit(p) i.e. log odd
# p.success    - posterior indicator if p > p.cut
# p.failure    - posterior indicator if p < p.cut
# pMix         - posterior mixture weight to test for "exchangeability"

#-------------------------------------------------------------------------------
  
  # prior distributions for EX-parameters
  for (jj in 1:Nexch) {
    mu[jj] ~dnorm(mu.mean[jj],mu.prec[jj])
    prior.tau.prec[jj] <- pow(tau.HN.scale[jj],-2)
    tau[jj] ~ dnorm(0,prior.tau.prec[jj]);I(0.001,)
    prec.tau[jj] <- pow(tau[jj],-2)
  }
  
  # log-odds parameters under EX
  for (jj in 1:Nexch) {
    for (j in 1:Nstrata) {
      re[jj,j] ~ dnorm(0,prec.tau[jj])
      LogOdds[jj,j] <- mu[jj]+re[jj,j]
    }
  }
  
  # log-odds parameters under NEX
  for (j in 1:Nstrata) {
    #p_Nmix[j] ~ dbeta(2,2) # slight mod to have flat prior
    #LogOdds[Nmix,j] ~ dnorm(nex.mean,nex.prec)#<- logit(p_Nmix[j])#

    # LogOdds[Nmix,j] ~ dt(0, 2, 1) #Student's t-distribution becomes the Cauchy distribution when the degrees of freedom is equal to one
    LogOdds[Nmix,j] ~ dunif(-20, 20)
    
  }
  
  # latent mixture indicators:
  # exch.index: categorial 1,...,Nmix=Nexch+1
  # exch: Nstrata x Nmix matrix of 0/1 elements
  for (j in 1:Nstrata) {
    exch.index[j] ~ dcat(pMix[1:Nmix,j])
    for (jj in 1:Nmix) {
      exch[j,jj] <- equals(exch.index[j],jj)
    }
  }
  
  # pick theta
  for (j in 1:Nstrata) {
    theta[j] <- LogOdds[exch.index[j],j]
  }
  
  # likelihood part
  for (i in 1:Nstrata) {
    logit( p[i] ) <- theta[i]
    p.success[i]  <- step(p[i]-p.cut)
    p.failure[i]  <- step(p.cut-p[i])
    r[i] ~ dbin(p[i],n[i])
    logit_p[i] <- theta[i]
  }

  
} # end of binary_exnex_model_fw

write.model(binary_exnex_model_fw, 'binary_exnex_model_fw.bug')

### Parameters to monitor
parameters_binary_exnex_model_fw <- c('p', 'logit_p', 'p.success', 'p.failure')

### Data similar to above with only difference in pMix

# data_binary_exnex_model_fw_pes <- binary_exnex_jag_fw_pes <- binary_exnex_mcmc_fw_pes <-
# data_binary_exnex_model_fw_opt <- binary_exnex_jag_fw_opt <- binary_exnex_mcmc_fw_opt <-
# data_binary_exnex_model_fw_neu <- binary_exnex_jag_fw_neu <- binary_exnex_mcmc_fw_neu <-list()
data_binary_exnex_model_fw <- binary_exnex_jag_fw <- binary_exnex_mcmc_fw <- list()

priors <- c('Pessimistic', 'Optimistic', 'Neutral')
colors <- c('gray', 'green', 'blue')
nsim <- 2e4

## Run JAGs
for (prior in priors) {
  data_binary_exnex_model_fw[[prior]] <- binary_exnex_jag_fw[[prior]] <-
  binary_exnex_mcmc_fw[[prior]]       <- list()
  
  pMix <- 
  case_when(
    prior=='Pessimistic' ~ c(1,0,0),
    prior=='Optimistic'  ~ c(0,1,0),
    prior=='Neutral'     ~ c(0,0,1)
  )
  
  pMix <- pMix %>% rep(Nmix) %>% matrix(nrow=Nmix, byrow = F)
  
  for (id in 1:length(obs.orrs)) {
    print(paste0(prior, 'Prior and Observed ORR = ', obs.orrs[id]))
    
    orr <- obs.orrs[id]
    n   <- c(data.use$n_a, npt)
    r   <- c(data.use$res_a, orr*npt) %>% round
    
    Nstrata <- n %>% length
    
    data_binary_exnex_model_fw[[prior]][[id]] <- list(
      pMix=pMix, Nexch=Nexch, Nmix=Nmix, Nstrata=Nstrata, n=n, r=r, 
      mu.mean=mu.mean, mu.prec=mu.prec, tau.HN.scale=tau.HN.scale,
      # nex.mean=nex.mean, nex.prec=nex.prec, 
      p.cut=p.cut
      )
    
    ### Inits
    inits_binary_exnex_model_fw <- function() {

      list(
        "mu"=rnorm(Nexch),
        "tau"=rnorm(Nexch) %>% abs
        )  
    } # end of inits_binary_exnex_model_fw  
    
    #### JAGS
    set.seed(36)
    binary_exnex_jag_fw[[prior]][[id]] <- jags(
      data = data_binary_exnex_model_fw[[prior]][[id]], 
      inits = inits_binary_exnex_model_fw, 
      parameters.to.save = parameters_binary_exnex_model_fw,
      model.file = "binary_exnex_model_fw.bug",
      n.chains=3, n.iter=1e4, n.burnin=5e3)
    # print(binary_exnex_jag_fw[[prior]])
    
    binary_exnex_mcmc_fw[[prior]][[id]] <- binary_exnex_jag_fw[[prior]][[id]] %>% as.mcmc.rjags
    binary_exnex_mcmc_fw[[prior]][[id]] %>% summary %>% print
    
    ### Credible interval for selected parameters
    mcmcplots::caterplot(binary_exnex_jag_fw[[prior]][[id]], parms = c('p'))  
    
    ### Density plot for posterior logit alone
    par(ask=F)
    mcmcplots::denplot(binary_exnex_jag_fw[[prior]][[id]], parms = c(paste0('logit_p[', Nstrata, ']')), collapse = T, lwd=2,xlim=c(-15,15), style ='plain', main='Posterior distribution of true ORR', frame.plot=F)
    # axis(1, seq(-15,15,5),
    #      labels=inv.logit(seq(-15,15,5)) %>% round(4), line=7)
    # mtext("ORR",1,line=9,at=0)    
    
  } # end of for (id in 1:length(obs.orrs))  
} # end of for (prior in priors)


```

### Summary of all outcomes

First plot all priors

```{r echo=TRUE, fig.height=8, fig.width=10} 
## Plot each prior distribution in the EX and NEX parts
prior_logit <- matrix(NA, nrow=Nmix, ncol=nsim)

## Simulate to plot Ex parts and plotting prior separately
for (j in 1:Nexch) {
  tau_j <- rhnorm(n = nsim, sigma = 1)
  mu_j  <- rnorm(n = nsim, mean = mu.mean[j], sd = 1/mu.prec[j])
  prior_logit[j,] <- sapply(1:nsim, function(x) {
    rnorm(1, mean=mu_j[x], sd=tau_j%>%sqrt)
  })
  tmp_dens <- prior_logit[j,] %>% density
  tmpcol <- col2rgb(colors[j])/255  
  par(mar=c(5.1, 4.1, 4.1, 2.1)+3)
  tmp_dens %>% plot(sub=NA, lwd=2, col=colors[j], 
                              ylim=c(0,.2), xlim=c(-15,15), frame.plot=F,
                              xlab='log-odd (logit) of ORR', 
                    main=paste(priors[j],
                               'Prior Distribution of True Log-Odd ORR (logit)'))
  tmp_dens %>% polygon(col=rgb(tmpcol[1],tmpcol[2],tmpcol[3],alpha=.5)) 
  segments(x0=mu.mean[j],x1=mu.mean[j],y0=0,y1=tmp_dens$y%>%max, col='black', 
           lty=2, lwd=2)  
  axis(1, seq(-15,15,5),
       labels=inv.logit(seq(-15,15,5)) %>% round(4), line=5)
  mtext("ORR",1,line=7,at=0)
} # end of for (j in 1:Nexch)

## Now for the NEX part
prior_logit[Nmix,] <- runif(nsim, -20, 20)
tmp_dens <- prior_logit[Nmix,] %>% density
tmpcol <- col2rgb(colors[Nmix])/255
par(mar=c(5.1, 4.1, 4.1, 2.1)+3)
tmp_dens %>% plot(sub=NA, lwd=2, col=colors[Nmix], 
                            ylim=c(0,.2), xlim=c(-15,15), frame.plot=F,
                            xlab='log-odd (logit)', 
                  main=paste(priors[Nmix],
                             'Prior Distribution of True Log-Odd ORR (logit)'))
tmp_dens %>% polygon(col=rgb(tmpcol[1],tmpcol[2],tmpcol[3],alpha=.5))
axis(1, seq(-15,15,5),
     labels=inv.logit(seq(-15,15,5)) %>% round(4), line=5)
mtext("ORR",1,line=7,at=0)

## Overlay all priors
par(mar=c(5.1, 4.1, 4.1, 2.1)+3)
for (j in 1:Nexch) {
  tmp_dens <- prior_logit[j,] %>% density
  if (j==1) tmp_dens %>% plot(sub=NA, lwd=2, col=colors[j], 
                              ylim=c(0,.2), xlim=c(-15,15), frame.plot=F,
                              xlab='log-odd (logit)', main='Prior Distribution of True Log-Odd ORR (logit)')
  # if (j>1) tmp_dens %>% lines(lwd=2, col=colors[j])
  tmpcol <- col2rgb(colors[j])/255
  tmp_dens %>% polygon(col=rgb(tmpcol[1],tmpcol[2],tmpcol[3],alpha=.5))
  
  segments(x0=mu.mean[j],x1=mu.mean[j],y0=0,y1=tmp_dens$y%>%max, col='black', 
           lty=2, lwd=2)
} # end of for (j in 1:Nexch)

## Simulate to plot NEX part
# x <- seq(-15,15, by=.001)
# x %>% dstp(mu=0, tau=2, nu=1) %>% lines(lwd=2, col=colors[Nmix])

tmpcol <- col2rgb(colors[Nmix])/255
prior_logit[Nmix,] %>% density %>% polygon(col=rgb(tmpcol[1],tmpcol[2],tmpcol[3],alpha=.5))
legend(10,.2, legend=priors, fill=colors)
axis(1, seq(-15,15,5),
     labels=inv.logit(seq(-15,15,5)) %>% round(4), line=5)
mtext("ORR",1,line=7,at=0)

# tmp2 <- rcauchy(nsim, location = 0, scale = 1) 
# tmp2 %>% density %>% lines(lwd=2, col=colors[Nmix])
# tmpcol <- col2rgb(Nmix)/255
# tmp2 %>% density %>% polygon(col=rgb(tmpcol[1],tmpcol[2],tmpcol[3],alpha=.5))
```



```{r echo=TRUE}
out_tab_p.success <- matrix(NA, ncol=obs.orrs %>% length, nrow=Nmix+1)
rownames(out_tab_p.success) <- c(priors, "Mix")
colnames(out_tab_p.success) <- obs.orrs


out_tab_p <- out_tab_logit <- out_tab_p.failure <- out_tab_p.success

for (id1 in 1:(Nmix+1)) {
  
  prior <- priors[id1]
  
  for (id2 in 1:length(obs.orrs)) {
    
    obs.orr <- obs.orrs[id2]
    
    if (id1<= Nmix) {
      out_tab_p.success[id1, id2] <- 
      binary_exnex_jag_fw[[prior]][[id2]]$BUGSoutput$mean$p.success[[Nstrata]]
      
      out_tab_p.failure[id1, id2] <- 
      binary_exnex_jag_fw[[prior]][[id2]]$BUGSoutput$mean$p.failure[[Nstrata]]      
      
      out_tab_logit[id1, id2] <- paste0(binary_exnex_jag_fw[[prior]][[id2]]$BUGSoutput$summary[Nstrata+1,1] %>% round(2), ' (',binary_exnex_jag_fw[[prior]][[id2]]$BUGSoutput$summary[Nstrata+1,3] %>% round(2),', ', binary_exnex_jag_fw[[prior]][[id2]]$BUGSoutput$summary[Nstrata+1,7] %>% round(2),')' ) 
      
      out_tab_p[id1, id2] <- paste0(binary_exnex_jag_fw[[prior]][[id2]]$BUGSoutput$summary[Nstrata*2+1,1] %>% round(2), ' (',binary_exnex_jag_fw[[prior]][[id2]]$BUGSoutput$summary[Nstrata*2+1,3] %>% round(2),', ', binary_exnex_jag_fw[[prior]][[id2]]$BUGSoutput$summary[Nstrata*2+1,7] %>% round(2),')' )       
      
    } else {
      out_tab_p.success[id1, id2] <- 
      binary_exnex_jag_dw[[id2]]$BUGSoutput$mean$p.success[[Nstrata]]  
      
      out_tab_p.failure[id1, id2] <- 
      binary_exnex_jag_dw[[id2]]$BUGSoutput$mean$p.failure[[Nstrata]]       
      
      out_tab_logit[id1, id2] <- paste0(binary_exnex_jag_dw[[id2]]$BUGSoutput$summary[Nstrata+1,1] %>% round(2), ' (',binary_exnex_jag_dw[[id2]]$BUGSoutput$summary[Nstrata+1,3] %>% round(2),', ', binary_exnex_jag_dw[[id2]]$BUGSoutput$summary[Nstrata+1,7] %>% round(2),')' ) 
      
      out_tab_p[id1, id2] <- paste0(binary_exnex_jag_dw[[id2]]$BUGSoutput$summary[Nstrata*2+1,1] %>% round(2), ' (',binary_exnex_jag_dw[[id2]]$BUGSoutput$summary[Nstrata*2+1,3] %>% round(2),', ', binary_exnex_jag_dw[[id2]]$BUGSoutput$summary[Nstrata*2+1,7] %>% round(2),')' )      
    } # end of if (id1<= Nmix) else ...

  } # end of for (id2 in 1:length(obs.orrs))
  
} # end of for (id1 in 1:(Nmix+1)) 

out_tab_p.success %>% kable(digits=2, caption = paste('Posterior probability of true ORR $>$', p.cut))  %>% kable_styling(full_width = F, position = 'center')

out_tab_p.failure %>% kable(digits=2, caption = paste('Posterior probability of true ORR $<$', p.cut))  %>% kable_styling(full_width = F, position = 'center')

out_tab_p %>% kable(digits=2, caption='Posterior mean and 95% credible interval for true ORR')  %>% kable_styling(full_width = F, position = 'center')

out_tab_logit %>% kable(digits=2, caption='Posterior mean and 95% credible interval for log-odd (logit) of true ORR')  %>% kable_styling(full_width = F, position = 'center')

# to-do: add summary table for Rhat and n_eff
```


## Association between LOR and LHR 

### Load data
```{r echo=TRUE}
data.raw <- readxl::read_xlsx(path = 'PRROC.xlsx', range = cell_cols('A:M'))
data.use <- data.raw %>% dplyr::filter(one_class_mod=='Y')

data.use %>% kbl() %>% kable_styling()

ns <- data.use %>% nrow
y  <- se <- matrix(NA, ncol=2, nrow=ns)

for (i in 1:ns) {
  s1 <- data.use$res_a[i]
  n1 <- data.use$n_a[i]
  
  s2 <- data.use$res_b[i]
  n2 <- data.use$n_b[i]  
  
  hr <- data.use$hr_pfs_ab[i]
  low<- data.use$hr_pfs_low[i]
  upp<- data.use$hr_pfs_upp[i]

  lor_sd <- lor.sd(s1,n1,s2,n2)
  lhr_sd <- lhr.sd(hr,low,upp)
  
  y[i,1:2]  <- c(lor_sd[1], lhr_sd[1])
  se[i,1:2] <- c(lor_sd[2], lhr_sd[2])
} # end of for (i in 1:ns)

## Naive linear plot
symbols(x=y[,1], y=y[,2], circle = (data.use$n_a+data.use$n_b)/pi, inches=1/3,
        ann=T, bg='steelblue2', fg=NULL, xlab='LOR', ylab='LHR')

lm(y[,2]~y[,1]) %>% abline(col='red', lwd=2)
```

### WinBUGs model for one treatment class

This is based on formulae (1) and (2) of https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7065251/

```{r echo=TRUE, fig.width=10, fig.height=10}

### Model definition 
bvnma_one_class_model <- function() {
## Data to be specify in the input
#-------------------------------------------------------------------------------
# ns    - number of studies
# y     - ns x 2 matrix, each row shows the treatment effect in the surrogate endpoint (1st element) and main endpoint (2nd element)
# se    - ns x 2 matrix, each row shows the (study-specific) se of the surrogate (1st element) and main endpoint (2nd element)
  
## Parameter to be monitored
# mu1
  
## Parameter to be monitored for surrogacy assessment
# lambda0     - intercept, ideally being 0
# lambda1     - slope, ideally >< 0
# big.psi.sq  - conditional variance, ideally being 0
#-------------------------------------------------------------------------------
  
  # within study precision matrix
  for(i in 1:ns) {
    prec_w[i,1:2,1:2] <- inverse(Sigma[i,1:2,1:2])
    # covariance matrix for the i-th study
    Sigma[i,1,1] <- pow(se[i,1], 2)
    Sigma[i,2,2] <- pow(se[i,2], 2)
    Sigma[i,1,2] <- se[i,1] * se[i,2] * rho_w#[i]
    Sigma[i,2,1] <- se[i,1] * se[i,2] * rho_w    
  }
  
  # Random effects model
  for(i in 1:ns) {
    y[i,1:2] ~ dmnorm(mu[i,1:2], prec_w[i,1:2,1:2])   
    
    # product normal formulation for the between study part
    mu[i,1] <- mu1[i]
    mu1[i]  ~ dnorm(0, a)
    # mu[i,1] <- dnorm(0, a)  
    mu[i,2] ~ dnorm(tmp[i], inv.big.psi.sq)
    tmp[i]  <- lambda0 + lambda1 * mu1[i]
    # tmp[i]  <- lambda0 + lambda1 * mu[i,1]
    
    #rho_w[i] <- dunif(-1, 1)
    y_new[i,1:2] ~ dmnorm(mu[i,1:2], prec_w[i,1:2,1:2]) 
  } # end of for(i in 1:ns)
  
  lambda0 ~ dnorm(0, a)
  lambda1 ~ dnorm(0, a)
  inv.big.psi.sq <- 1/ big.psi.sq # putting 1/big.psi.sq directly into dnorm(,) not work!
  big.psi.sq <- abs(tmp2)
  tmp2 ~ dnorm(0, b)# dnorm(0, b)I(0,) # the latter form does not work!
  rho_w ~ dunif(-1,1) #-.05 #dunif(-1,1) # giving rho_w prior either not work or not converge
  a <- 0.001
  b <- 2
  
  # # predict Y2 for given Y1
  # for(i in 1:nn) { #nn is number of new y1n
  #   y2n ~ dnorm(mu2n, pre2n)
  #   m2n <- mu
  # }

} # end of bvnma_one_class_model

write.model(bvnma_one_class_model, 'bvnma_one_class_model.bug')

### Parameters to monitor
parameters_one_class_model <- c('mu1', 'lambda0', 'lambda1','big.psi.sq', 
                                'rho_w', 'y_new')

# ns <- 5 # number of studies

### Inits
inits_one_class_model <- function() {

  list(
    "mu1"= rnorm(ns, 0, 1),
    # "mu"= c(rnorm(5, 0, 1), rep(NA, 5)) %>% matrix(nrow=5, byrow = F),
    "lambda0"= rnorm(1, 0, 1),
    "lambda1"= rnorm(1, 0, 1),
    "big.psi.sq"= rnorm(1, 0, 1) %>% abs,
    # rho_w=runif(5, -1, 1)
    "rho_w"=runif(1, -1, 1)
    )  
} # end of inits_one_class_model

### Data
# data_one_class_model <- list(
#   "ns"=ns,
#   "y"=c(1.46, 2.17, 1.1, 2.22, 0.58, 1.29, 1.41, 2.63, 1.36, 3) %>%  matrix(nrow=ns, byrow = T),
#   "se"= c(.24, .21, .23, .2, .23, .22, .22, .25, .19, .2) %>%  matrix(nrow=ns, byrow = T)
# )
data_one_class_model <- list(ns=ns, y=y, se= se)

### Run MCMC
set.seed(36)
bvnma_one_class_bug <- bugs(data = data_one_class_model, inits = 
                            inits_one_class_model, parameters.to.save = 
                            parameters_one_class_model, 
                            model.file = "bvnma_one_class_model.bug",
                            n.chains=3, n.iter=20e4,
                            clearWD=T, bugs.directory="C:/Users/nguyea37/Documents/WinBUGS14")
print(bvnma_one_class_bug)
plot(bvnma_one_class_bug)

# ### Convergence diagnostic plot
# mcmcplots::mcmcplot(bvnma_one_class_bug)

### Credible interval for selected parameters
par(mar=c(5.1, 4.1+3, 4.1, 2.1))
mcmcplots::caterplot(bvnma_one_class_bug, parms = c('lambda0', 'lambda1','big.psi.sq'), labels=c('lambda_0\n Intercept \n ideally being 0', 'lambda_1\n Slope\n ideally < 0',
       'psi^2\n Conditional variance\n ideally being 0'), reorder = F, frame.plot=F, style='plain')

### Density plot for selected parameters
mcmcplots::denplot(bvnma_one_class_bug, parms = c('lambda0', 'lambda1','big.psi.sq'), collapse = T, 
main=c('$\\lambda_0$ - Intercept, ideally being 0', '$\\lambda_1$ - Slope, ideally >< 0',
       '$\\psi^2$  - conditional variance, ideally being 0'), style = 'plain', frame.plot=F)


# ### Convert Bug obj to MCMC obj so more function can work with
# bvnma_one_class_mcmc <- bvnma_one_class_bug %>% as.mcmc.bugs
# 
# bvnma_one_class_mcmc %>% geweke.plot
# 
# bvnma_one_class_mcmc %>% gelman.plot
# 
# bvnma_one_class_mcmc %>% autocorr.plot
# 
# bvnma_one_class_bug %>% autoplot

## Naive linear plot plus simulation from posterior predictive dist
library(randomcoloR)
cols <- distinctColorPalette(ns)
# symbols(x=y[,1], y=y[,2], circle = (data.use$n_a+data.use$n_b)/pi, inches=1/3,
#         ann=T, bg=cols[id], fg=NULL, xlab='LOR', ylab='LHR', 
#         ylim=c(-3,3), xlim=c(-3,3))

plot(x=y[,1], y=y[,2], cex=(data.use$n_a+data.use$n_b)/(pi*30),
       xlab='Log Odds-Ratio', ylab='Log Hazards-Ratio', ylim=c(-3,3), xlim=c(-3,3), pch=19, col=cols,
     main='Observed data (big circles withe size ~ N) and simulated data (tiny dots) \n from posterior predictive distribution for each trial (by color)', frame.plot = F)

lor_all <- lhr_all <- NULL

for(id in 1:ns) {
  lor <- bvnma_one_class_bug$sims.list$y_new[,id,1]
  lhr <- bvnma_one_class_bug$sims.list$y_new[,id,2]
  points(x=lor, y=lhr, col=cols[id], cex=.33, pch=1)
  
  lor_all <- c(lor_all, lor)
  lhr_all <- c(lhr_all, lhr)
}
lm(y[,2]~y[,1]) %>% abline(col='black', lwd=1.75, lty=2)
legend(x=-3,y=3, legend=data.use$des, col = cols, pch=19, bty='n')

# lm(lhr~lor) %>% abline(col='black', lwd=1.5, lty=2)

```

